Visualizing Contingency Tables

### 2006-09-15 trunk/vcd/paper/Shadings/JCGS.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@568 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{abstract}
Residual-based shadings for enhancing mosaic and association plots
to visualize independence models for contingency tables are extended
in two directions: (a)~perceptually uniform Hue-Chroma-Luminance colors are used and (b)~the
result of an associated significance test is coded by the appearance of
color in the visualization. For obtaining (a), a general strategy for
deriving diverging palettes in the perceptually-based HCL space is suggested. As for (b),
cut offs that control the appearance of color are computed in a data-driven
way based on the conditional permutation distribution of maximum-type
test statistics. The shadings are first established for the case of independence
in 2-way tables and then extended to more general independence models
for multi-way tables, including in particular conditional independence
models.\\[0.3cm]

>>>>

\begin{abstract}
Residual-based shadings for enhancing mosaic and association plots
to visualize independence models for contingency tables are extended
in two directions: (a)~perceptually uniform Hue-Chroma-Luminance (HCL)
colors are used and (b)~the
result of an associated significance test is coded by the appearance of
color in the visualization. For obtaining (a), a general strategy for
deriving diverging palettes in the perceptually-based HCL space is suggested. As for (b),
cut offs that control the appearance of color are computed in a data-driven
way based on the conditional permutation distribution of maximum-type
test statistics. The shadings are first established for the case of independence
in 2-way tables and then extended to more general independence models
for multi-way tables, including in particular conditional independence
models.\\[0.3cm]
